Simulating High-Dimensional Multivariate Data

### 2020-11-11 030-bigsimr-package.Rmd
2nd draft. Polish ch040 figures and tables

```{r ch030-basic-example-setup, echo=TRUE, message=FALSE}
library(bigsimr)
library(tidyverse)
library(patchwork)
```

@@

```{r ch030-aq-joint-dist, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap="Bivariate scatterplot of Ozone vs. Temperature with estimated marginal densities. The data are left skewed tails and appear to be correlation."}

>>>>

```{r ch030-basic-example-setup, echo=TRUE, message=FALSE, cache=F}
library(bigsimr)
library(tidyverse)
library(patchwork)
```

@@

```{r ch030-aq-joint-dist, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap="Bivariate scatterplot of Ozone vs. Temperature with estimated marginal densities. The data are left skewed tails and appear to be correlation.", cache=F}

### 2020-11-11 040-monte-carlo-evaluation.Rmd
2nd draft. Revise MC chapter v3
2nd draft. Polish ch040 figures and tables

| Simulation Reps ($B$) | Correlation Types | Distribution |
|---------------------|:------------------:|--------------:|
|$\{ 1000, 10000, 100000 \}$ | $\{ \rho_P, \rho_S, \tau \}$ | $\{ { \bf Y} \sim MVN( \mu= 0 , \sigma = 1, \rho ), \\ { \bf Y} \sim MVG( shape = 10, rate = 1, \rho ), \\ { \bf Y} \sim MVNB(p = `r prob`, r = 4,\rho) \}$. |

For each of the unique 9 simulation configurations above, we estimate the correlation bounds and vary $\rho$ along a sequence of 100 points evenly placed within the bounds (minus an adjustment factor $\epsilon=0.01$ to handle numeric issues when the bound is specified exactly).

@@

@@

```{r ch040-biMAEtable, results='asis'}
## tabMSE  <- allDat %>%
##    group_by( N, margins ) %>%
##    summarize( mse = mean( ( rho - rho_hat )^2 ) )
tabMSE  <- allDat %>%
    ## filter( N == 100000) %>%
    group_by( N, type, margins ) %>%
##     summarize( mse = mean( ( rho - rho_hat )^2 ) ) %>%
    summarize( MAE = mean( abs( rho - rho_hat )  ) )
## normMSE <- as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ] ) 
## ( tabMSE$mse - normMSE ) / normMSE
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) )
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) ) / tabMSE$mse
knitr::kable(tabMSE,
             col.names = c("No. of random vectors",
                           "Correlation type",
                           "Distribution",
                           "Mean abs. error"),
             booktabs = TRUE,
             caption = 'Average abolute error in matching the target dependency across the entire range of possible correlations for each bivariate marginal.'
)
```

>>>>

@@

| Simulation Reps ($B$) | Correlation Types | Identical-margin 2D distribution |
|-------------|:--------------:|----------------------:|
|$1000$ | Pearson ($\rho_P$) | ${ \bf Y} \sim MVN( \mu= 0 , \sigma = 1, \rho )$ |
|$10,000$ | Spearman ($\rho_S$) | ${ \bf Y} \sim MVG( shape = 10, rate = 1, \rho )$ |
| $100,000$| Kendall ($\tau$)| ${ \bf Y} \sim MVNB(p = `r prob`, r = 4,\rho)$ |

For each of the unique 9 simulation configurations above, we estimate the correlation bounds and vary $\rho$ along a sequence of 100 points evenly placed within the bounds (minus an adjustment factor of $\epsilon=0.01$ to handle numeric issues when the bound is specified exactly).

@@

```{r ch040-biMAEtable, results='asis', cache=F}
## tabMSE  <- allDat %>%
##    group_by( N, margins ) %>%
##    summarize( mse = mean( ( rho - rho_hat )^2 ) )
tabMSE  <- allDat %>%
    ## filter( N == 100000) %>%
    group_by( N, type, margins ) %>%
##     summarize( mse = mean( ( rho - rho_hat )^2 ) ) %>%
    summarize( MAE = mean( abs( rho - rho_hat )  ) )
## normMSE <- as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ] ) 
## ( tabMSE$mse - normMSE ) / normMSE
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) )
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) ) / tabMSE$mse

knitr::kable(tabMSE,
             format = 'latex',
             col.names = c("No. of random vectors",
                           "Correlation type",
                           "Distribution",
                           "Mean abs. error"),
             booktabs = TRUE,
             caption = 'Average abolute error in matching the target dependency across the entire range of possible correlations for each bivariate marginal.',
             linesep = c('', '',  '\\addlinespace')
)
```

### 2020-11-11 050-examples.Rmd
2nd draft. Polish ch040 figures and tables

```{r ch050-readBRCA, echo=FALSE, eval=TRUE}
## full workflow simulating RNA-seq data
## brcaRDS <- 'data/brca95.rds'
## myProb = 0.95
brca <- readRDS(file = brcaRDS)
## smaller set for prototyping
## d=5
## brca <- brca[ , 1:d]
```

>>>>

```{r ch050-readBRCA, echo=FALSE, eval=TRUE, cache=F}
## full workflow simulating RNA-seq data
## brcaRDS <- 'data/brca95.rds'
## myProb = 0.95
brca <- readRDS(file = brcaRDS)
## smaller set for prototyping
## d=5
## brca <- brca[ , 1:d]
```
